%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Machine Learning Scientist} % Job title
    {Inari Agriculture} % Organisation
    {Cambridge, MA} % Location
    {Jan 2019 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Co-led a four-person team developing a BERT-based protein language model to discover novel stability-enhancing mutations for improving efficiency of CRISPR-Cas proteins for genome editing in plants.}
        \item {Developed epistasis-aware DNA and protein language models to identify and prioritize high-impact deleterious mutations in sequenced corn varieties for correction via genome editing.}
        \item {Developed an approach using an ensemble of language models and bioinformatic methods to compute zero-shot predictions of the impact of complex mutations on endogenous protein function.}
        \item {Co-led a team of co-op students to develop the \href{https://assets-eu.researchsquare.com/files/rs-1927200/v1_covered.pdf}{first genomic language model} used for predicting tissue-specific gene expression in plants.}
        \item {Implemented internal-facing pipelines for non-computational lab scientists to run AlphaFold2/3 on proprietary protein sequences.}
        \item {Implemented a transfer learning approach to enrich single-cell RNA-seq data in data-poor species via joint embeddings with related species, and then infer tissue-specific gene regulatory networks.}
        \item {Developed a method for discovering causal interventions for trait improvement in soybean by scaling up AlphaFold2 for many-by-many protein-protein interaction screening.}
        \item {Mentored 8+ junior colleagues and interns, attended multiple conferences, facilitated meetings with scientific advisors, filed 5+ patents.}
%        \item {\textbf{Technical Skills:} Python, PyTorch, TensorFlow, Docker, AWS, Bioinformatics.}
%        \item {\textbf{Soft Skills:} Rapid Prototyping, Literature Review, Teamwork, Scientific Communication.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Fellow} % Job title
    {Insight Data Science} % Organisation
    {Boston, MA} % Location
    {Sept 2018 - Dec 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Implemented a \href{https://github.com/knowbodynos/wikontext}{Word2Vec model} to enhance Wikipedia page previews by displaying the most relevant information to the current page.}
        \item {Used Wikipedia's bi-directional clickstream data to validate a 17\% increase in relevance over default page previews.}
        \item {Built a \href{https://www.wikontext.us/}{Chrome browser extension} served using a jQuery/Flask/AWS stack to achieve high performance on real-time, client-side data.}
%        \item {\textbf{Technical Skills:} Python, Flask, JavaScript.}
%        \item {\textbf{Soft Skills:} Rapid prototyping, Teamwork.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Graduate Research Assistant} % Job title
    {Northeastern University} % Organisation
    {Boston, MA} % Location
    {Sept 2011 - May 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
%        \item {\textbf{Advisor:} Brent D. Nelson}
        \item {Designed a modular, distributed \href{http://github.com/knowbodynos/stringmods}{algorithm} in C++/Python to systematically compute type-IIB string theory vacuum states on an HPC cluster.}
    %		\item {Developed a \href{http://github.com/knowbodynos}{data-processing engine} optimized for resource constraints of a shared computing cluster.}
        \item {Compiled the \href{https://app.box.com/s/ch4w5gy1wv9dv11ptf314u7ovj2x4vig}{world's largest database} of $10^5$ string theory vacua, resulting in discovery of candidate universes extending the Standard Model.} % (35 GB).
        \item {Estimated the number of vacua ($>10^{(10^{4})}$) in the string landscape using deep neural networks using specialized ``equation learner'' layers.}
        \item {Built and maintained a \href{http://www.rossealtman.com/toriccy/}{queryable web UI} with MongoDB backend based on feedback from stakeholders in the string theory community.}
        \item {Co-founded the String Data group for ML applied to string theory, leading to international conferences and collaboration with industry.}
    %		\item {Trained and advised other researchers as a senior research group member.}
    %		\item {Coordinated with many collaborators across the US, Europe, Asia, and Africa.}
%        \item {\textbf{Technical Skills:} Python, Keras, MongoDB, High-performance computing.}
%        \item {\textbf{Soft Skills:} Independent Research, Scientific Communication.}
      \end{cvitems}
    }

%%---------------------------------------------------------
%  \cventry
%    {Graduate Research Assistant} % Job title
%    {Rensselaer Polytechnic Institute} % Organisation
%    {Troy, NY} % Location
%    {Sept 2010 - May 2011} % Date(s)
%    {
%      \begin{cvitems} % Description(s) of tasks/responsibilities
%%        \item \textit{Advisor:} Shengbai Zhang
%        \item {Researched the band gap properties of photovoltaic materials for use in improved solar cells.}
%        \item {Investigated the unusual band gap properties of chalcopyrite (CuFe${\rm S}_{2}$).}
%      \end{cvitems}
%    }
%
%%---------------------------------------------------------
%  \cventry
%    {Graduate Research Assistant} % Job title
%    {Cornell University} % Organisation
%    {Ithaca, NY} % Location
%    {Sept 2009 - May 2010} % Date(s)
%    {
%      \begin{cvitems} % Description(s) of tasks/responsibilities
%%        \item {\textit{Advisor:} Richard V. E. Lovelace}
%        \item {Authored code to simulate realistic stellar occultations, generate corresponding ground intensity data, and recover amplitude and phase data.}
%      \end{cvitems}
%    }
%
%%---------------------------------------------------------
%  \cventry
%    {Undergraduate Research Assistant} % Job title
%    {Cornell University} % Organisation
%    {Ithaca, NY} % Location
%    {June 2007 - August 2007} % Date(s)
%    {
%      \begin{cvitems} % Description(s) of tasks/responsibilities
%%        \item {\textit{Advisor:} Saul Teukolsky}
%        \item {Co-authored code for an ongoing project to simulate comptationally difficult relativistic astronomical scenarios such as binary black hole systems.}
%      \end{cvitems}
%    }
%
%%---------------------------------------------------------
%  \cventry
%    {Research Intern} % Job title
%    {Stony Brook University} % Organisation
%    {Stony Brook, NY} % Location
%    {June 2003 - May 2005} % Date(s)
%    {
%      \begin{cvitems} % Description(s) of tasks/responsibilities
%%        \item {\textit{Advisor:} Nancy Goroff}
%        \item {Authored code to interface with MacroModel conformation calculations and determine the energetically stable states of complex macromolecules.}
%        \item {Investigated most energetically favorable techniques for constructing kekulene on a cyclodextrin scaffold.}
%      \end{cvitems}
%    }

%---------------------------------------------------------
\end{cventries}
